Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-07-06 paper/revision/responseToReviewers.tex

$\rightarrow$
Since the tasks are different, it is not straightforward to compare the proposed methods with the approaches of ref\#36. In the former, we propose a method for acoustic scene similarity retrieval, while the latter discusses the problem of scene classification. In similarity retrieval, we would like to find other recordings in the dataset that are as similar to the original as possible (which here is defined as being in the same class). In scene classification, the task is to assign a class to each recording. In this sense, similarity retrieval is a more general problem. For our experiments, we calculate the p@k curves for each proposed method, allowing us to analyze the distribution of recordings most similar to a particular query recording. The classification setting is reproduced for $k = 1$, with the p@1 measure corresponding to the leave-one-out classification accuracy of nearest neighbors. As such, the classification task is a special case of the similarity retrieval setting considered here. We have modified the manuscript to make this distinction more clear.

It is also worth considering that the BOF model is used differently in scene retrieval (our use case) and scene classification (ref\#36). In scene retrieval, given two scenes (a and b) modeled using GMMs (A and B), the similarity between two scenes is the similarity between A and B. In scene classification, each class of sound scenes (park, boulevard) are modeled using a GMM (P, B). Then, for an unknown scene $u$, the likelihood of $u$ given P and B are computed. The scene $u$ is then labeled P if the likelihood of $u$ given P is greater than the likelihood of $u$ given B.

Even if the technical aspects are quite close, the way the algorithm is designed is different as the tasks they have to solve are differents. A synthetic description of the matter is added to Section 2.

\item \emph{.P1L36: "superiority" and other superlative seems too strong. I would say that the proposed approach performed better on the dataset tested.}

$\rightarrow$ VL $\checkmark$

\item \emph{.P2L29: "cannot be trusted" seems too strong, any system is prone to errors. These errors need to be estimated so that we can estimate how much the system is reliable, but I would not roughly say that it cannot be trusted.}

### 2018-07-06 paper/lostanlenRelevanceScattering.tex
remove "cannot be trusted"
rename "Algorithm" subsection
e.g. -> \eg{}

An important problem is that manually analysing the recorded data to identify the quantities of interest is very costly. Some sort of pre-screening is therefore required to reduce the need for human expert listening and annotation.

The most straightforward approach is to specify a closed set of sound classes, such as sounds classes expected to appear near the acoustic sensors. Computational models are then trained  for these classes which are used to automatically annotate recordings~\cite{quteprints96243}. A given time interval (e.g., a single day) is then represented by the number of events detected during that interval for each class. This allows the scientist to drastically reduce the amount of information requiring manual processing. However, this approach has two drawbacks. First, it relies on trained models whose behavior on unseen data (such as different sensors) is prone to errors and cannot be trusted. Second, and more importantly, it is based on \textit{a priori} knowledge and thus cannot be considered for exploratory analysis where quantities of interest have yet to be defined.

@@

It is worth mentionning that this task typically falls into a unsupervised paradigm where no prior knowldge is used to model a given scene. For each scene $s$, a model is compute $M_s$ is computed. The similarity among the scene $s_1$ and $s_2$ is computed as the similarity, see Section~\ref{sec:experiments} for further details. The BOF approach is also widely used in a supervised fashion for solving a classification task~\cite{7100934}. In this case, each class of scenes of a given typology, say \{park, boulevard, square \}, is modeled by a GMM trained on scenes taken from a training set. In order to predict the class of a given scene $s$, the likelihood each model given the scene are computed. The scene is then labeled park if the likelihood of the GMM trained on park scenes is higher than the other likelihoods.

@@

\subsection{Algorithm}

>>>>

An important problem is that manually analysing the recorded data to identify the quantities of interest is very costly. Some sort of pre-screening is therefore required to reduce the need for human expert listening and annotation.
To this aim, the most straightforward approach is to specify a closed set of sound classes, such as sounds classes expected to appear near the acoustic sensors. Computational models are then trained  for these classes which are used to automatically annotate recordings~\cite{quteprints96243}. A given time interval (\eg{} a single day) is then represented by the number of events detected during that interval for each class. This allows the scientist to drastically reduce the amount of information requiring manual processing. However, this approach has two drawbacks. First, it relies on trained models whose behavior on unseen data (such as different sensors) is prone to errors. Second, and more importantly, it is based on \textit{a priori} knowledge and thus cannot be considered for exploratory analysis where quantities of interest have yet to be defined.

@@

It is worth mentionning that this task typically falls into a unsupervised paradigm where no prior knowldge is used to model a given scene. For each scene $s$, a model is compute $M_s$ is computed. The similarity among the scene $s_1$ and $s_2$ is computed as the similarity, see Section~\ref{sec:experiments} for further details. The BOF approach is also widely used in a supervised fashion for solving a classification task~\cite{7100934}. In this case, each class of scenes of a given typology, say \{\emph{park, boulevard, square }\}, is modeled by a GMM trained on scenes taken from a training set. In order to predict the class of a given scene $s$, the likelihood each model given the scene are computed. The scene is then labeled park if the likelihood of the GMM trained on park scenes is higher than the other likelihoods.

@@

\subsection{Evaluation and algorithm}
